Title

### 2014-07-17 paper.tex
model generation

We sampled 320 comments from the historical data of code reviews in the Qt project.
We then classified the samples as either useful (that is, technically contributing to the code) or not useful.
This task is carried out by three people who worked independently.

>>>>

We sampled 320 comments from the data set.
These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
This task is carried out by three people who worked independently.

Each comment is then scored based on the number of positive answers.
For example, a comment with a score of 3 means that all three people said that it is useful,
while a comment with a score of 0 means that none of us marked it as useful.

%The score of a comment can be defined as:

%\begin{align*}
%Score_i & = \sum_{\text{reviewer } r} Review(r, i). \\
%Review(r, i) & = \begin{cases}
%	1 & \text{if } r \text{ says that the comment } i \text{ is useful,} \\
%	0 & \text{otherwise.}
%\end{cases}
%\end{align*}

\subsection{Model Generation}

% the metrics
For each comment, we computed a similarity and dissimilarity metrics
between the comment text and the corresponding commit message.
We chose cosine similarity and euclidean distance as the metrics to use in model generation.

% assumptions in categorization
The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also have tried using the `or' operator. We found that using `and' produces better result.}

% finding parameters
To find these parameters, we used a brute-force approach.
